### 2014-10-09 writing/AAAI SSS '15/wordnet.tex

% Can a model to do this with something that has the scale and structure of a real vocabulary?

>>>>

We have shown that a model can learn to reason using relations over a small artificial dataset, 
but it the question of whether the same model can show this behavior over the type and number of
relations seen in a real natural language vocabulary.

Unfortunately, we are aware of no reliable source of relation data that covers a large natural 
language vocabulary using the natural logic relations discussed above. However, WordNet 
\cite{fellbaum2010wordnet} provides a different type of lattice structure which is compatible with
our learning paradigm.

We extract three types of relation from WordNet. \ii{Hypernym} and \ii{hyponym} can be are represented
directly in the WordNet graph structure, and correspond closely to the \natrev and \natfor relations from
natural logic. As in natural logic, these relations are mirror images of one another: if \ii{dog} is a
hyponym of \ii{animal}, then \ii{animal} must be a hypernym of \ii{dog}.
